\ttitle

### 2015-08-18 main.tex
CPET Jaundice - Major update
- Next few commits will be following Donny chat this morning
Huge commit following on from Donny conversation
- Change all references to before period
- Remove post 2011/2012 references from introduction - one 2012 reference left was published online in Aug 2011
- Rename title - 'investigation into clinical utility of CPET'
- Remove hyphenation of words
- Left justify with ragged right edge
- Remove bold formatting in some tables
- Minor grammar and style corrections in multiple places
- Change reference Chandrabalan 2013 to Chapter 2
- Create some new tables for b

\textbf{Chapter \ref{ch_cpet_outcomes}} reports on the role of cardiopulmonary exercise testing in predicting postoperative complications after pancreaticoduodenectomy. The results demonstrate that patients with $\dot{V}_{O_2}$AT less than 10 ml/kg/min are more likely to develop a postoperative pancreatic fistula, stay longer in hospital and less likely to receive adjuvant therapy. These results emphasise the importance of excellent aerobic fitness to recover from the operative stress of major surgery without significant morbidity. Cardiopulmonary exercise testing may prove useful in selecting patients for intensive prehabilitation programmes as well as for other optimisation measures to prepare them for major surgery.

@@

Professor Paul Horgan,\\
University Department of Surgery, Glasgow Royal Infirmary
}

@@

% Include the chapters of the thesis as separate files from the Chapters folder
\input{Chapters/Introduction} 		%1
\input{Chapters/CPET_Outcomes} 	%2
\input{Chapters/CPET_Jaundice} 	%3
\input{Chapters/BodyComp}			%4
\input{Chapters/CPET_Survival}		%5
\input{Chapters/CRP_Complications}	%6
\input{Chapters/Discussion}		%7

>>>>

\textbf{Chapter \ref{ch_cpet_outcomes}} reports on the role of cardiopulmonary exercise testing in predicting postoperative complications after pancreaticoduodenectomy. The results demonstrate that patients with $\dot{V}_{O_2}$AT less than 10 ml/kg/min are more likely to develop a postoperative pancreatic fistula, stay longer in hospital and less likely to receive adjuvant therapy. These results emphasise the importance of aerobic fitness to recover from the operative stress of major surgery without significant morbidity. Cardiopulmonary exercise testing may prove useful in selecting patients for intensive prehabilitation programmes as well as for other optimisation measures to prepare them for major surgery.

@@

Professor Paul Horgan,\\
University Department of Surgery, Glasgow Royal Infirmary

Mr. Euan J Dickson,
West of Scotland Pancreatic Unit, Glasgow Royal Infirmary
}

@@

% Include the chapters of the thesis as separate files from the Chapters folder
%\input{Chapters/Introduction} 		%1
%\input{Chapters/CPET_Outcomes} 	%2
%\input{Chapters/CPET_Jaundice} 	%3
\input{Chapters/BodyComp}			%4
%\input{Chapters/CPET_Survival}		%5
%\input{Chapters/CRP_Complications}	%6
%\input{Chapters/Discussion}		%7
